---
title: "Comments codering"
author: "Shy-Ann Moehamatdjalil"
date: "14-5-2021"
output: html_document
---

# DEPENDS ON: Data/Comments/comment_overview.xlsx , Data/Comments/Kopie van Twijfelgevallen_LB.xlsx, 
#             Data/Comments/Twijfelgevallen Combined AANGEPAST.xlsx

# CREATES: Data/Comments/Twijfelgevallen.xlsx, Data/Comments/Twijfelgevallen Combined.xlsx, Data/comment_overview_V1.xlsx
#          Data/Extra analyse/comment_overview_ZT.xlsx

## Load packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidytext)
library(readxl)
library(writexl)
```

## Load Data
```{r message=FALSE}
# Load in the data
comment_overview <- read_excel("./Data/Comments/comment_overview.xlsx", col_types = "text") %>% 
  mutate(across(!c("user_name","comment","ma_sentiment", 'twijfel',
                   "replies","id"), as.numeric))

comment_overview %>% head()
```

## Make seperate file with the comments that are twijfelgevallen

Next, select the comments that have the NegCon or PosCon sentiment and the ones that are a debatble case in which that column also has a value. Write that dataframe to an Excel file

```{r}
comments_rand <- comment_overview %>% 
  filter(ma_sentiment %in% c("NegCon", "PosCon") | !is.na(twijfel)) 

comments_rand %>% 
  write_xlsx("./Data/Comments/Twijfelgevallen.xlsx")
```


## Combine file with annotated comments of second annator

File of myself with debatable comments combined with Laura's annotated. Compared to each other and adjusted in Excel
```{r}
# Load file from R
comments_LB <- read_excel("./Data/Comments/Kopie van Twijfelgevallen_LB.xlsx")

# Combine the two documents and write to excel
comments_LB %>% 
  select(sk_id, ma_sentiment_LB, `Toelichting Laura`) %>% 
  merge(comments_rand, by = 'sk_id') %>% 
  write_xlsx("./Data/Comments/Twijfelgevallen Combined.xlsx")
```

Next, combine the new file with adjusted comments to the original document

```{r}
# Load file back in from Excel
comments_combined <- read_excel("./Data/Comments/Twijfelgevallen Combined AANGEPAST.xlsx")

# Add the columns from the data frame to original so that the columns are the same for both dataframes 
comment_overview_V1 <- comment_overview %>% 
  add_column(context = 'Sentiment', .after = "twijfel") %>% 
  add_column(ma_sentiment_LB = 'Sentiment', .after = "context") %>% 
  add_column(`Toelichting Laura` = 'Sentiment')

# Add the rows from the file with the combined sentiment categories
comment_overview_V1 [comment_overview_V1$sk_id %in% comments_combined$sk_id,] <- comments_combined

# Check if everything worked and write to excel
comment_overview_V1 %>% head()
comments_overview_FI <- comment_overview_V1 %>% 
   select(-c(twijfel, context, ma_sentiment_LB,`Toelichting Laura`))

# Final dataframe
comments_overview_FI %>% 
    write_xlsx("./Data/comment_overview_V1.xlsx")
```

#### EXTRA ANALYSIS ###

## Make a dataframe without the debatable comments
```{r}
comment_overview_ZT <- comment_overview[!comment_overview$sk_id %in% comments_rand$sk_id,] #2582, 254 comments excluded

# Write to excel
comment_overview_ZT %>% 
  write_xlsx("./Data/Extra analyse/comment_overview_ZT.xlsx")
```

